Traffic Aware Resource Allocation Schemes for Multi-Cell \acs{MIMO}-\acs{OFDM} Systems

### 2015-01-28 Report/appendix_tightness.tex
halfcooked

In order for the constraints \eqref{eqn-6.2} and \eqref{eqn-6.3} to be active, there should be at least one user per \ac{BS} with large enough backlogged packets that cannot be satisfied with the given power budget. To prove this, let us consider a single \ac{BS} \me{N_T \times 1} system with \me{|U|_b} users each with \me{Q_k} backlogged packets. Let us consider the problem for a single \ac{BS} \me{b} as 
\begin{IEEEeqnarray}{rCl}
	\underset{\gamma_{k},\mvec{m}{k},\beta_{k}}{\text{minimize}} &\quad& \sum_{k \in \mc{U}_b} \big | Q_k - \log_2(1 + \gamma_k) \big |^q  \eqsub \\
	\text{subject to} &\quad& \gamma_{k} \leq \frac{ | \mvec{H}{k} \mvec{m}{k}|^2}{\beta_{k}} \IEEEyessubnumber \label{ae-1} \\
	&\quad& \beta_{k} \geq N_0 + \sum_{\mathclap{i \neq k}} |\mvec{H}{k} \mvec{m}{i} |^2 \IEEEyessubnumber \label{ae-2} \\
	&\quad& \sum_{k \in \mc{U}_b} \text{tr} \, (\mvec{m}{k} \mvec{m}{k}^\herm) \leq P_{{\max}}. \IEEEyessubnumber \label{ae-3}
\end{IEEEeqnarray}
Let us assume the system has \me{N_T > |\mc{U}_b|} and the precoders are determined for all users at the optimal point for which the objective is minimum and is nonzero. Let us consider two users, say \me{i} and \me{j} with precoders \me{\mvec{m}{i}} and \me{\mvec{m}{j}}. In order to show the tightness of the constraints \eqref{ae-1} and \eqref{ae-2}, let us assume by contradiction that \eqref{ae-1} and \eqref{ae-2} are not tight for a user \me{i} only. Let us also consider that \me{\gamma_k} for all users \me{k \in \mc{U}_b \backslash j} are identified to satisfy the backlogged packets.

@@

Since the allocated rate of user \me{j} is less than the queued packets, we can find a precoder \me{\mvec{m}{j}} with the additional power of \me{\Delta P} as \me{\mvec{m}{j}^\prime = \bar{\mbf{m}}_{j} + \mvec{V}{j} \mbf{e}^\prime}. Note that the new precoder has no impact on the interference constraint of other users. The newly found precoder \me{\mvec{m}{j}^\prime} minimize the queue of user \me{j} without affecting the rates of other user, there by reduces the objective further. It is in contradiction to our original assumption that the precoders are optimal and the objective is minimum. It can be seen that the constraints are tight as long as there is one user with unserviced backlogged packets at each \ac{BS} with the given power budget. Since the objective is not to minimize the power, when the power budget is more than sufficient to service the backlogged packets of all users, the \ac{JSFRA} scheme is not guaranteed to find the minimum power precoders to minimize the current backlogged packets in the system.

>>>>

In order for the constraints \eqref{eqn-6.2} and \eqref{eqn-6.3} to be active, there should be at least one user per \ac{BS} with large enough backlogged packets that cannot be satisfied with the given power budget. To prove this, let us consider a single \ac{BS} \me{N_T \times 1} system with \me{|U|_b} users each with \me{Q_k} backlogged packets. Let us consider the problem for a single \ac{BS} \me{b} as 
\begin{IEEEeqnarray}{rCl}
	\underset{\gamma_{k},\mvec{m}{k},\beta_{k}}{\text{minimize}} &\quad& \sum_{k \in \mc{U}_b} \big | Q_k - \log_2(1 + \gamma_k) \big |^q  \eqsub \\
	\text{subject to} &\quad& \gamma_{k} \leq \frac{ | \mvec{H}{k} \mvec{m}{k}|^2}{\beta_{k}} \IEEEyessubnumber \label{ae-1} \\
	&\quad& \beta_{k} \geq N_0 + \sum_{\mathclap{i \neq k}} |\mvec{H}{k} \mvec{m}{i} |^2 \IEEEyessubnumber \label{ae-2} \\
	&\quad& \sum_{k \in \mc{U}_b} \trace \, (\mvec{m}{k} \mvec{m}{k}^\herm) \leq P_{{\max}}. \IEEEyessubnumber \label{ae-3}
\end{IEEEeqnarray}
Let us assume the system has \me{N_T > |\mc{U}_b|} and the precoders are determined for all users at the optimal point for which the objective is minimum and is nonzero. Let us consider two users, say \me{i} and \me{j} with precoders \me{\mvec{m}{i}} and \me{\mvec{m}{j}}. In order to show the tightness of the constraints \eqref{ae-1} and \eqref{ae-2}, let us assume by contradiction that \eqref{ae-1} and \eqref{ae-2} are not tight for a user \me{i} only. Let us also consider that \me{\gamma_k} for all users \me{k \in \mc{U}_b \backslash j} are identified to satisfy the backlogged packets.

@@

Since the allocated rate of user \me{j} is less than the queued packets, we can find a precoder \me{\mvec{m}{j}} with the additional power of \me{\Delta P} as \me{\mvec{m}{j}^\prime = \bar{\mbf{m}}_{j} + \mvec{V}{j} \mbf{e}^\prime}. Note that the new precoder has no impact on the interference constraint of other users. The newly found precoder \me{\mvec{m}{j}^\prime} minimize the queue of user \me{j} without affecting the rates of other user, there by reduces the objective further. It is in contradiction to our original assumption that the precoders are optimal and the objective is minimum.

It can be seen that the constraints are tight as long as there is one user with unserviced backlogged packets at each \ac{BS} with the given power budget. Since the objective is not to minimize the power, when the power budget is more than sufficient to service the backlogged packets of all users, the \ac{JSFRA} scheme is not guaranteed to find the minimum power precoders to empty the current backlogged packets in the system. The objective of the \ac{JSFRA} problem can be regularized by including the power term to find the minimum power precoders as
\begin{equation*}
\| \tilde{\mbf{v}} \|_q + \varphi \sum_{b \in \mc{B}} \sum_{k \in \mc{U}_b} \sum_{n = 1}^{N} \sum_{l=1}^{L} \mathrm{tr} \left ( \mvec{m}{l,k,n} \mbf{m}^\herm_{l,k,n} \right ),
\end{equation*}
for a small \me{\varphi} without affecting the optimal solution. Note that the above objective is guaranteed to make the constraints \eqref{eqn-6.2} and \eqref{eqn-6.3} active by relaxing the power constraint \eqref{eqn-6.4}.

### 2015-01-28 Report/convergence_centralized.tex
halfcooked

\newcommand{\eqn}[1]{\(#1\)}
\newcommand{\mx}{\mbf{x}}
\newcommand{\my}{\mbf{y}}
\newcommand{\mz}{\mbf{z}}
\newcommand{\mxb}{{{\mbf{x}}}}
\newcommand{\myb}{{{\mbf{y}}}}
\newcommand{\iterate}[2]{{#1}^{(#2)}}
\newcommand{\iter}[3]{{#1}_{#2}^{(#3)}}

\subsubsection{Centralized Problem}

Let us express the \ac{JSFRA} problem in \eqref{eqn-6} and \eqref{eqn-mse-1} as
\begin{IEEEeqnarray}{rCl} \label{con}
\underset{\mx,\my,\mz}{\text{minimize}} &\quad& f(\mx,\my,\mz) \eqsub \label{con-obj} \\
\text{subject to} &\quad& h(\mz) - g_0(\mx,\my) \leq 0 \eqsub \label{con-dc} \\
&\quad& g_1(\mx,\my) \leq 0, \eqsub \label{con-cvx-blk} \\
&\quad& g_2(\mx) \leq 0, \eqsub \label{con-cvx}
\end{IEEEeqnarray}
wher \me{g_2,f} are convex functions and \me{h} is a linear function. Let \me{g_0,g_1} are convex functions only on \me{\mx} or \me{\my} as the variable but not on both. Note that the \eqref{con-dc} correspond to the constraints in \eqref{eqn-6.2} and \eqref{eqn-mse-1.2} and \eqref{con-cvx-blk} corresponds to the constraints in \eqref{eqn-6.3} and \eqref{eqn-mse-1.3}. Other convex constraints are addressed by the constraint \eqref{con-cvx}. With this, the feasible set of the problem \eqref{con} is given by 
\begin{IEEEeqnarray}{rl}
\mc{F} &= \{ \mx,\my,\mz | h(\mz) - g_0(\mx,\my) \leq 0, g_1(\mx,\my) \leq 0, g_2(\mx) \leq 0\} \nonumber
\end{IEEEeqnarray}

@@

Finally, to prove the global convergence of the objective, we need to show the nonincreasing behavior of the objective function between each \ac{AO} update, \textit{i.e}, 
\begin{equation*}
f(\iter{\mx}{\ast}{i},\iter{\my}{\ast}{i},\iter{\mz}{\ast|x}{i}) \leq f(\iter{\mx}{\ast}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{\ast|y}{i}).
\end{equation*}
Let us consider an \ac{AO} iteration \me{i} in which the optimal value for \eqn{\mx} and \eqn{\mz} are obtained as \me{\iter{\mx}{\ast}{i}} and \me{\iter{\mx}{\ast|y}{i}} using fixed \eqn{\my = \iter{\my}{\ast}{i-1}}. In order to find \me{\iter{\my}{\ast}{i}}, we fix \eqn{\mx} as \me{\iter{\mx}{\ast}{i}} and optimize for \me{\my}. Since the problem \eqref{con} is nonconvex even after fixing \me{\mx}, we have to linearize the convex function in the \ac{DC} constraint \eqref{con-dc} around some fixed operating point of \me{\my}. Since we know that \me{\iter{\my}{\ast}{i-1}} is already a feasible point for \me{\my} along with \me{\iter{\mx}{\ast}{i}}, linearization is performed around this feasible point. Using the inequality in \eqref{con-sub-set}, we can show that \eqn{\{\iter{\my}{\ast}{i-1},\iter{\mx}{\ast}{i},\iter{\mz}{\ast|y}{i}\} \in \iter{\mc{Y}}{0}{i}}. Now the optimization is performed to find the optimal \me{\my} using the relaxed subproblem \eqref{con-m}, the optimal solution \me{\iter{\mz}{0}{i}} for the initial iteration after \ac{AO} update follows
\begin{equation*}
f(\iter{\mx}{\ast}{i},\iter{\my}{0}{i},\iter{\mz}{0}{i}) \leq f(\iter{\mx}{\ast}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{\ast|x}{i}),
\end{equation*}
since the feasible set includes the earlier optimal points \eqn{\{\iter{\my}{\ast}{i-1},\iter{\mx}{\ast}{i}\}} as the operating point for \ac{AO} and \ac{SCA} iteration. Note that it is not possible to say \me{\iter{\mc{X}}{\ast}{i} \subseteq \iter{\mc{Y}}{0}{i}}, since the set is nonconvex on \me{\mx,\my}, but \eqn{\{\iter{\my}{\ast}{i-1},\iter{\mx}{\ast}{i},\iter{\mz}{\ast|y}{i}\} \in \{ \iter{\mc{X}}{\ast}{i} \cap \iter{\mc{Y}}{0}{i} \}}. Now by using induction, we can show that the global problem converges to a feasible point of the nonconvex problem \eqref{con} in a nonincreasing manner.

>>>>

\newcommand{\eqn}[1]{\(#1\)}
\newcommand{\mx}{\mbf{x}}
\newcommand{\my}{\mbf{y}}
\newcommand{\mz}{\mbf{z}}
\newcommand{\mxb}{{{\mbf{x}}}}
\newcommand{\myb}{{{\mbf{y}}}}
\newcommand{\iterate}[2]{{#1}^{(#2)}}
\newcommand{\iter}[3]{{#1}_{#2}^{(#3)}}
Let us express the \ac{JSFRA} problem in \eqref{eqn-6} and \eqref{eqn-mse-1} as
\begin{IEEEeqnarray}{rCl} \label{con}
\underset{\mx,\my,\mz}{\text{minimize}} &\quad& f(\mx,\my,\mz) \eqsub \label{con-obj} \\
\text{subject to} &\quad& h(\mz) - g_0(\mx,\my) \leq 0 \eqsub \label{con-dc} \\
&\quad& g_1(\mx,\my) \leq 0, \eqsub \label{con-cvx-blk} \\
&\quad& g_2(\mx) \leq 0, \eqsub \label{con-cvx}
\end{IEEEeqnarray}
wher \me{g_2,f} are convex functions and \me{h} is a linear function. Let \me{g_0,g_1} are convex functions only on \me{\mx} or \me{\my} as the variable but not on both. Note that the \eqref{con-dc} correspond to the constraints in \eqref{eqn-6.2} and \eqref{eqn-mse-1.2} and \eqref{con-cvx-blk} corresponds to the constraints in \eqref{eqn-6.3} and \eqref{eqn-mse-1.3}. Other convex constraints are addressed by the constraint \eqref{con-cvx}. With this, the feasible set of the problem \eqref{con} is given by 
\begin{IEEEeqnarray}{rl}
\mc{F} &= \{ \mx,\my,\mz | h(\mz) - g_0(\mx,\my) \leq 0, g_1(\mx,\my) \leq 0, g_2(\mx) \leq 0\} \nonumber
\end{IEEEeqnarray}

@@

Finally, to prove the global convergence of the objective, we need to show the nonincreasing behavior of the objective function between each \ac{AO} update, \textit{i.e}, 
\begin{equation*}
f(\iter{\mx}{\ast}{i},\iter{\my}{\ast}{i},\iter{\mz}{\ast|x}{i}) \leq f(\iter{\mx}{\ast}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{\ast|y}{i}).
\end{equation*}
Let us consider an \ac{AO} iteration \me{i} in which the optimal value for \eqn{\mx} and \eqn{\mz} are obtained as \me{\iter{\mx}{\ast}{i}} and \me{\iter{\mx}{\ast|y}{i}} using fixed \eqn{\my = \iter{\my}{\ast}{i-1}}. In order to find \me{\iter{\my}{\ast}{i}}, we fix \eqn{\mx} as \me{\iter{\mx}{\ast}{i}} and optimize for \me{\my}. Since the problem \eqref{con} is nonconvex even after fixing \me{\mx}, we have to linearize the convex function in the \ac{DC} constraint \eqref{con-dc} around some fixed operating point of \me{\my}. Since we know that \me{\iter{\my}{\ast}{i-1}} is already a feasible point for \me{\my} along with \me{\iter{\mx}{\ast}{i}}, linearization is performed around this feasible point. Using the inequality in \eqref{con-sub-set}, we can show that \eqn{\{\iter{\my}{\ast}{i-1},\iter{\mx}{\ast}{i},\iter{\mz}{\ast|y}{i}\} \in \iter{\mc{Y}}{0}{i}}. Now the optimization is performed to find the optimal \me{\my} using the relaxed subproblem \eqref{con-m}, the optimal solution \me{\iter{\mz}{0}{i}} for the initial iteration after \ac{AO} update follows
\begin{equation*}
f(\iter{\mx}{\ast}{i},\iter{\my}{0}{i},\iter{\mz}{0}{i}) \leq f(\iter{\mx}{\ast}{i},\iter{\my}{\ast}{i-1},\iter{\mz}{\ast|x}{i}),
\end{equation*}
since the feasible set includes the earlier optimal points \eqn{\{\iter{\my}{\ast}{i-1},\iter{\mx}{\ast}{i}\}} as the operating point for \ac{AO} and \ac{SCA} iteration. Note that it is not possible to say \me{\iter{\mc{X}}{\ast}{i} \subseteq \iter{\mc{Y}}{0}{i}}, since the set is nonconvex on \me{\mx,\my}, but \eqn{\{\iter{\my}{\ast}{i-1},\iter{\mx}{\ast}{i},\iter{\mz}{\ast|y}{i}\} \in \{ \iter{\mc{X}}{\ast}{i} \cap \iter{\mc{Y}}{0}{i} \}}. Now by using induction, we can show that the global problem converges to a feasible point of the nonconvex problem \eqref{con} in a nonincreasing manner\footnote{Note that the objective is monotonically decreasing even if the \ac{SCA} subproblem \eqref{con-m} is terminated after predetermined number iterations or for certain accuracy.}.

### 2015-01-28 Report/convergence_distributed.tex
halfcooked

The \ac{ADMM} decomposition method is based on the \acl{DD}, however it shows better convergence properties. In contrast to the \acl{PD} problem, the \ac{ADMM} method relaxes the interference constraints by including it in the objective function of each subproblem with a penalty pricing \cite{palomar2006tutorial,boyd2011distributed}. In order to decouple the problem \eqref{eqn-decent-1}, the coupling variables \me{\zeta_{l,k,n,b}} in \eqref{eqn-decent-3} are replaced by the respective local copies \me{\mbfa{\zeta}^{\set{b}}, \forall b \in \mc{B}}, which are then solved for an optimal solution. Now the sub problems are coupled by the global consensus vector \me{\mbfa{\zeta}} maintaining the complete stacked  interference profile of all users in the system as
\begin{IEEEeqnarray}{ll}
\mbfa{\zeta} &= \left [ \zeta_{1,\bar{\mc{U}}_{1}(1),1,1}, \dotsc, \zeta_{L,\bar{\mc{U}}_{1}(1),1,1}, \dotsc, \zeta_{L,\bar{\mc{U}}_{1}(|\bar{\mc{U}}_{1}|),1,1}, \right. \nonumber \\
& \left . \dotsc, \zeta_{L,\bar{\mc{U}}_{N_B}(|\bar{\mc{U}}_{N_B}|),1,N_B}, \dotsc, \zeta_{L,\bar{\mc{U}}_{N_B}(|\bar{\mc{U}}_{N_B}|),N,N_B} \right ] \eqspace \IEEEyessubnumber \\
n_{b_k} &= |\mbfa{\zeta}^{\set{b_k}}| = N L \sum_{b \in \mc{B}} \left | \bar{\mc{U}}_b\right |. \IEEEyessubnumber
\end{IEEEeqnarray}

Let \me{\mbfa{\zeta}(b_k)} denote the consensus entries corresponding to \ac{BS} \me{b_k}. Let \me{\mbfa{\nu}^{\set{b_k}}} represent the stacked dual variables corresponding to the equality condition \me{\mbfa{\zeta}^{\set{b_k}} = \mbfa{\zeta}(b_k)} used in the subproblems. In order to limit the local interference assumptions \me{\zeta^{\set{b_k}}_{l,k,n,b}} in \ac{BS} \me{b_k}, the \ac{ADMM} method augments a scaled quadratic penalty of the interference deviation between the local and consensus value for the interference from the \ac{BS} \me{b} as \me{\zeta_{l,k,n,b}} in the objective function. At optimality, the locally assumed and the consensus interference values will be equal,  providing no contribution to the objective function. The optimal step size used to update the dual variables is the scaling factor \me{\rho} used to scale the penalty term in the objective function \cite{boyd2011distributed,bertsekas1999nonlinear}. The equality constraint for the local and the consensus interference vector \me{\mbfa{\zeta}^{\set{b_k}} = \mbfa{\zeta}(b_k)} present in each subproblem is relaxed by the taking the partial Lagrangian. Now, the subproblem at \ac{BS} \me{b} for the \me{\ith{i}} iteration is given by
\iftoggle{single_column}{\allowdisplaybreaks
\begin{IEEEeqnarray}{rCl} \label{eqn-dual-3}
\underset{\substack{\gamma_{l,k,n}, \mvec{W}{k,n},\mvec{M}{k,n} \\ \beta_{l,k,n}, \mbfa{\zeta}^{\set{b}(i)}}}{\text{minimize}} &\quad & \| \tilde{\mbf{v}}_{b} \|_q + \mbfa{\nu}^{{\set{b}(i-1)}T} \left ( \mbfa{\zeta}^{\set{b}(i)} - \mbfa{\zeta}^{(i-1)}(b) \right ) + \frac{\rho}{2} \Big \| \, \underbrace{\mbfa{\zeta}^{\set{b}(i)}}_{\text{local}} - \underbrace{\mbfa{\zeta}^{(i-1)}(b)}_{\text{consensus}} \, \Big \|^2_2 \IEEEyessubnumber \label{eqn-dual-3a} \\
\text{subject to} && \beta_{l,k,n} \geq \sum_{\substack{j = 1\\j \neq l}}^L |\mvec{w}{l,k,n}^\herm \mvec{H}{{b},k,n} \mvec{m}{j,k,n} |^2 + \sum_{{\hat{b}} \in \bar{\mc{B}}_{b}} \zeta^{\set{b}(i-1)}_{l,k,n,{\hat{b}}} \nonumber \\
&& \qquad {} \qquad {} + \sum_{i \in \mc{U}_{b} \backslash \{k\}} \sum_{j = 1}^L |\mvec{w}{l,k,n}^\herm \mvec{H}{{b},k,n} \mvec{m}{j,i,n} |^2 + \enoise \IEEEyessubnumber \label{eqn-dual-1d} \\
&& \zeta^{\set{b}(i)}_{\pr{l},\pr{k},n,{b}} \geq \sum_{k \in \mc{U}_{\hat{b}}} \sum_{l = 1}^L |\mvec{w}{\pr{l},\pr{k},n}^\herm \mvec{H}{b,\pr{k},n} \mvec{m}{l,k,n} |^2 \; \forall \pr{k} \in \bar{\mc{U}}_{b}, \; \forall n \in \mc{N} \IEEEyessubnumber \label{eqn-dual-1e} \\
&\quad& \eqref{eqn-8} \; \text{and} \; \eqref{eqn-4.3}, \IEEEyessubnumber \label{eqn-dual-1f}
\end{IEEEeqnarray}
}{{\allowdisplaybreaks
\begin{IEEEeqnarray}{rCl} \label{eqn-dual-3}
	\underset{\substack{\gamma_{l,k,n}, \mvec{W}{k,n},\mvec{M}{k,n} \\ \beta_{l,k,n}, \mbfa{\zeta}^{\set{b}(i)}}}{\text{minimize}} && \| \tilde{\mbf{v}}_{b} \|_q + \mbfa{\nu}^{{\set{b}(i-1)}T} \left ( \mbfa{\zeta}^{\set{b}(i)} - \mbfa{\zeta}^{(i-1)}(b) \right )  \nonumber \\
	&& + \frac{\rho}{2} \Big \| \, \underbrace{\mbfa{\zeta}^{\set{b}(i)}}_{\text{local}} - \underbrace{\mbfa{\zeta}^{(i-1)}(b)}_{\text{consensus}} \, \Big \|^2_2 \IEEEyessubnumber \label{eqn-dual-3a}  \\
	\text{subject to} &\quad& \nonumber \\
	\beta_{l,k,n} \geq \sum_{\mathclap{j = 1,j \neq l}}^L && |\mvec{w}{l,k,n}^\herm \mvec{H}{{b},k,n} \mvec{m}{j,k,n} |^2 + \sum_{{\hat{b}} \in \bar{\mc{B}}_{b}} \zeta^{\set{b}(i-1)}_{l,k,n,{\hat{b}}} \nonumber \\
	+ \sum_{i \in \mc{U}_{b} \backslash \{k\}} \sum_{j = 1}^L && |\mvec{w}{l,k,n}^\herm \mvec{H}{{b},k,n} \mvec{m}{j,i,n} |^2 + \enoise \IEEEyessubnumber \eqspace \label{eqn-dual-1d} \\
	\zeta^{\set{b}(i)}_{\pr{l},\pr{k},n,{b}} \geq \sum_{k \in \mc{U}_{\hat{b}}} && \sum_{l = 1}^L |\mvec{w}{\pr{l},\pr{k},n}^\herm \mvec{H}{b,\pr{k},n} \mvec{m}{l,k,n} |^2, \forall \pr{k} \in \bar{\mc{U}}_{b} \IEEEyessubnumber \eqspace \label{eqn-dual-1e} \\
	&& \eqref{eqn-8} \; \text{and} \; \eqref{eqn-4.3}, \IEEEyessubnumber \label{eqn-dual-1f}
\end{IEEEeqnarray}}}
where the superscript \me{i} represents the current iteration or the information exchange index and \me{\mbfa{\zeta}^{(i-1)}} denotes the updated global interference level from the \me{\ith{(i-1)}} information exchange of the local interference vector \me{\mbfa{\zeta}^{\set{b}(i-1)}, \forall b \in \mc{B}}.

Now, the local problem \eqref{eqn-dual-3} at each \ac{BS} \me{b} is solved either by the \ac{SCA} approach discussed in Section \ref{sec-3.2.1} or by using the \ac{MSE} reformulation approach outlined in Section \ref{sec-3.3}. Once the local problems are solved at each \ac{BS}, the new update for the global interference vector \me{\mbfa{\zeta}^{(i)}} and the dual variables \me{\mbfa{\nu}^{\set{b}(i)}} are performed at each \ac{BS} independently by exchanging the corresponding local copies of the interference vector \me{\mbfa{\zeta}^{\set{b}(i)}, \forall b \in \mc{B}}. Since the entries in \me{\mbfa{\zeta}^{(i)}} relate exactly to two \acp{BS} only, each entry in \me{\mbfa{\zeta}^{(i)}} can be updated by exchanging the local copies from the corresponding two \acp{BS}. For instance, the entry \me{\zeta^{(i)}_{l,\mc{U}_{b_k}(1),n,b}} depends on the local interference value \me{\zeta^{\set{b_k}(i)}_{l,\mc{U}_{b_k}(1),n,b}} assumed by the \ac{BS} \me{b_k} and the actual interference caused by \ac{BS} \me{b} as in \me{\zeta^{\set{b}(i)}_{l,\mc{U}_{b_k}(1),n,b}} as
\begin{equation}
\zeta_{l,\mc{U}_{b_k}(1),n,b}^{(i)} = \frac{1}{2} \, \left ( \, \zeta^{\set{b}(i)}_{l,\mc{U}_{b_k}(1),n,b} + \zeta^{\set{b_k}(i)}_{l,\mc{U}_{b_k}(1),n,b} \, \right ).
\label{zeta_update}
\end{equation}
The dual variable vector \me{\mbfa{\nu}^{\set{b_k}}}, which includes the stacked dual variables of the interference equality constraint at \ac{BS} \me{b_k}, are updated using the subgradient as
\begin{equation}\label{dual-sg-update}
\nu^{\set{b_k}(i)}_{l,k,n,b} = \nu^{\set{b_k}(i-1)}_{l,k,n,b} + \rho \, \left (\zeta^{\set{b_k}(i)}_{l,k,n,b} - \zeta^{(i)}_{l,k,n,b} \right ).
\end{equation}
The distributed precoder design using \ac{ADMM} approach is shown in Algorithm \ref{algo-3}.
{\allowdisplaybreaks 
\begin{algorithm}
	\SetAlgoLined
	\DontPrintSemicolon
	\BlankLine
	\SetKwInput{KwInit}{Initialize}
	\KwIn{\me{a_k, \, Q_k, \, \mvec{H}{b,k,n},\; \fall b \in \mathcal{B}, \, \fall k \in \mathcal{U}, \fall n \in \mathcal{N}}}
	\KwOut{\me{\mvec{m}{l,k,n}} and \me{\mvec{w}{l,k,n} \fall l \in \set{1,2,\dotsc,L}}}
	\KwInit{\me{i=0} and the transmit precoders \me{\tilde{\mbf{m}}_{l,k,n}} randomly satisfying total power constraint \eqref{eqn-4.3}}
	update \me{\mvec{w}{l,k,n}} with \eqref{eqn-10} and \me{\tilde{\mbf{u}}_{l,k,n}} with \eqref{eqn-8} \;
	initialize the global interference vectors \me{\mbfa{\zeta}^{(0)} = \mbfa{0}^{\mathrm{T}}} \;
	initialize the interference threshold \me{\mbfa{\nu}^{\set{b}(0)} \forall b \in \mc{B} = 0} \;
	\ForEach{\ac{BS} \me{b \in \mc{B}}}{
		\Repeat{convergence or \me{i \geq I_{\max}}}{
			initialize \me{j=0} \;
			\Repeat{convergence or \me{j \geq J_{\max}}}{
				solve for \me{\mvec{m}{l,k,n}} and the local interference \me{\mbfa{\zeta}^{\set{b}}} using \eqref{eqn-dual-3} \;
				exchange \me{\mbfa{\zeta}^{\set{b}(j)}} among \acp{BS} in \me{\mc{B}} \;
				update dual variables in \me{\mbfa{\nu}^{\set{b}(j+1)}} using \eqref{dual-sg-update}\;
				update the consensus vector \me{\mbfa{\zeta}^{(j+1)}} using \eqref{zeta_update}\;
				\me{j = j + 1}\;
			}
			downlink precoded pilot transmission with \me{\mvec{m}{k,n}}\;
			update \me{\mvec{l}{k,n}} and notify to all \acp{BS} in \me{\mc{B}} using uplink precoded pilots as in \cite{komulainen2013effective}\;
			update \me{{\mbf{u}}_{l,k,n}} using \eqref{eqn-6.3} and \eqref{eqn-wsrm-expr} for \ac{SCA} or \me{\tilde{\epsilon}_{l,k,n}} using \eqref{eqn-mse-1.3} for \ac{MSE} approach \;
			$i = i + 1$ \;
		}
	}
	\caption{Distributed \ac{JSFRA} scheme using \ac{ADMM}}
	\label{algo-3}
\end{algorithm}}

\begin{comment}
\subsubsection*{Convergence}
The convergence of the \ac{ADMM} method follows the same argument as the centralized algorithm if each distributed algorithm is allowed to converge to a stationary value for the fixed \ac{SCA} point. Since the subproblem solved at each \ac{BS} is convex, the \ac{ADMM} method converges to a stationary point \cite{boyd2011distributed} for the fixed \ac{SCA} value. The receive beamformers are updated along with the \ac{SCA} update of \me{\tilde{\mbf{u}}_{l,k,n}}. Combining the receiver update with the \ac{SCA} update improves the convergence speed due to the fact that the \ac{MMSE} receivers are optimal for the fixed transmit beamformers, providing monotonic increase in the objective function.
\end{comment}

>>>>

The convergence of the \ac{ADMM} method follows the same argument as the centralized algorithm if each distributed algorithm is allowed to converge to a stationary value for the fixed \ac{SCA} point. Since the subproblem solved at each \ac{BS} is convex, the \ac{ADMM} method converges to a stationary point \cite{boyd2011distributed} for the fixed \ac{SCA} value. The receive beamformers are updated along with the \ac{SCA} update of \me{\tilde{\mbf{u}}_{l,k,n}}. Combining the receiver update with the \ac{SCA} update improves the convergence speed due to the fact that the \ac{MMSE} receivers are optimal for the fixed transmit beamformers, providing monotonic increase in the objective function.
